---
title: "Belen Rugerio"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(dplyr)
library(fivethirtyeight)
# For reading CSV spreadsheet files:
library(readr)
```

## Fall 2021

My first semester of senior year I took **SDS 192: Introduction to Data Science**. Over the course of the semester we learned about many topics, from data wrangling to data visualization. The following is an overview of the coursework I completed for the class. 

## Data Wrangling

The following is a data wrangling exercise using data from the Titanic about survivors. 


This code downloads ths csv file and wrangles the data to display a table showing the count of surivors and the numer of desceased. 
```{r }
titanic <- read_csv("https://rudeboybert.github.io/SDS192/static/PS/titanic.csv")

survival <- titanic %>% group_by(Survived) %>%  count(Survived)
survival <- rename(survival, Count=n) 
survival
```
Now that dataframe is further grouped by sex to differentiate the survivors by gender assigned at birth. 
```{r}
survival_by_sex <- titanic %>% group_by(Sex) %>% count(Survived) 
survival_by_sex <- rename(survival_by_sex, Count=n)  
survival_by_sex
```


## Data Visualization

The following is a barplot showing the campaign stops for the 2016 presidential candidates from September to Noveber, obtained from the package fivethirtyeight. 

```{r pressure, echo=FALSE}
library(ggplot2)
library(dplyr)
library(fivethirtyeight)
library(moderndive)
library(lubridate)

weekly_campaign_stops <- pres_2016_trail %>% 
  mutate(week = floor_date(date, unit = "week")) %>% group_by(candidate, week) %>% 
  summarize(number_of_stops = n())

ggplot(data = weekly_campaign_stops, mapping = aes(x = week, y = number_of_stops, fill = candidate)) +
  geom_col()+ facet_wrap(~ candidate, ncol = 1)+ggtitle("Weekly Campaign Stops in 2016") +
  xlab("Week") + ylab("Number of stops")+theme(legend.position="bottom")
```

